---
title: "p8105_hw1_jz3425"
author: "Jibei Zheng"
date: 9/25/2021
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1

__Create a data frame comprised of 4 vectors:__

```{r problem_1}
set.seed(1)

#create a data frame comprised of 4 vectors
my_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = c(letters[1:10]),
  vec_factor = factor(c(rep("R", 3), rep("G", 3), rep("B", 4)))
)

my_df
```

The mean of the numeric vector is `r mean(pull(my_df, vec_numeric))`.

The mean of the logical vector is `r mean(pull(my_df, vec_logical))`.

The mean of the character and factor vector doesn't work.


__Convert variables from one type to another:__

```{r convert, eval = FALSE}
#convert ligical vector to numeric
as.numeric(pull(my_df, vec_logical))

#convert character vector to numeric, but this doesn't work
as.numeric(pull(my_df, vec_char))

#convert factor vector to numeric
as.numeric(pull(my_df, vec_factor))
```

The logical vector is converted to numeric, as TRUE= 1 and FALSE = 0.

The characters cannot be converted, so the mean is not calculable.

The factor vector was converted to numeric and the mean is `r mean(as.numeric(pull(my_df, vec_factor)))`, however it means nothing.

# Problem 2

```{r problem_2}
#load the "penguins" dataset
data("penguins", package = "palmerpenguins")
```

__Short description:__

This dataset includes data of `r nrow(penguins)` penguins and `r ncol(penguins)` variables of them: `r names(penguins)`.

Among all the penguins, there are `r nlevels(pull(penguins, names(penguins[1])))` kinds of `r names(penguins[1])`: `r levels(pull(penguins, names(penguins[1])))`, coming from `r nlevels(pull(penguins, names(penguins[2])))` different `r names(penguins[2])`s: `r levels(pull(penguins, names(penguins[2])))`.

The mean of `r names(penguins[5])` is `r mean(pull(penguins, names(penguins[5])), na.rm = TRUE)`.

__Make a scatter plot:__

```{r scatter_plot, warning = FALSE}
#make a scatter plot of flipper_length_mm (y) vs bill_length_mm (x)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

```{r save_pdf, eval = FALSE}
#save my scatter plot
ggsave("penguins_scatter_plot.pdf", height = 4, width = 6)
```

