---
title: "p8105_hw1_jz3425"
author: "Jibei Zheng"
date: 9/25/2021
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1

__create a data frame comprised of 4 vectors:__

```{r data_frame}
set.seed(1)

#create a data frame comprised of 4 vectors
my_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = c(letters[1:10]),
  vec_factor = factor(c(rep("R", 3), rep("G", 3), rep("B", 4)))
)

my_df
```

The mean of the numeric vector is `r mean(pull(my_df, vec_numeric))`.

The mean of the logical vector is `r mean(pull(my_df, vec_logical))`.

The mean of the character and factor vector doesn't work.


__Convert variables from one type to another:__

```{r eval = FALSE}
#convert ligical vector to numeric
as.numeric(pull(my_df, vec_logical))

#convert character vector to numeric, but this doesn't work
as.numeric(pull(my_df, vec_char))

#convert factor vector to numeric
as.numeric(pull(my_df, vec_factor))
```

The logical vector is converted to numeric, as TRUE= 1 and FALSE = 0.

The characters cannot be converted, so the mean is not calculable.

The factor vector was converted to numeric and the mean is `r mean(as.numeric(pull(my_df, vec_factor)))`, however it means nothing.